Practical Effects of Integrating Temperature with Strang Split Reactions

### 2021-02-19 strang/paper.tex
add e integration results
some paper work

\begin{document}
%======================================================================
% Title
%======================================================================
%\title{A Simplified Spectral Deferred Correction Method for Coupling Hydrodynamics with Reaction Networks and Nuclear Statistical Equilibrium}
\title{Practical Effects of Integrating Temperature / Energy with Strang Split Reactions}

@@

%======================================================================
% Abstract and Keywords
%======================================================================
\begin{abstract}
Folks should integrate energy with their reactions!
\end{abstract}

@@

\clearpage

\begin{deluxetable}{lllllll}
\tablecaption{\label{table:react_convert_no_T} Convergence ($L_1$ norm) for the reacting convergence with no $T$ integration.}
\tablehead{\colhead{field} & \colhead{$\epsilon_{64 \rightarrow 128}$} & 
           \colhead{rate} & \colhead{$\epsilon_{128\rightarrow 256}$} & 
           \colhead{rate} & \colhead{$\epsilon_{256\rightarrow 512}$}}
\startdata
 $\rho$                      & $2.735 \times 10^{18}$  & 2.057  & $6.571 \times 10^{17}$  & 2.474  & $1.183 \times 10^{17}$  \\
 $\rho u$                    & $6.729 \times 10^{26}$  & 2.416  & $1.260 \times 10^{26}$  & 2.699  & $1.941 \times 10^{25}$  \\
 $\rho v$                    & $6.729 \times 10^{26}$  & 2.416  & $1.260 \times 10^{26}$  & 2.699  & $1.941 \times 10^{25}$  \\
 $\rho E$                    & $2.513 \times 10^{35}$  & 2.226  & $5.372 \times 10^{34}$  & 2.169  & $1.195 \times 10^{34}$  \\
 $\rho e$                    & $2.292 \times 10^{35}$  & 2.194  & $5.011 \times 10^{34}$  & 2.253  & $1.051 \times 10^{34}$  \\
 $T$                         & $2.321 \times 10^{21}$  & 1.606  & $7.623 \times 10^{20}$  & 1.993  & $1.915 \times 10^{20}$  \\
 $\rho X(\isotm{He}{4})$     & $2.806 \times 10^{18}$  & 2.028  & $6.880 \times 10^{17}$  & 2.432  & $1.275 \times 10^{17}$  \\
 $\rho X(\isotm{C}{12})$     & $1.807 \times 10^{17}$  & 1.846  & $5.026 \times 10^{16}$  & 1.605  & $1.653 \times 10^{16}$  \\
 $\rho X(\isotm{O}{16})$     & $1.905 \times 10^{14}$  & 1.500  & $6.737 \times 10^{13}$  & 1.439  & $2.484 \times 10^{13}$  \\
 $\rho X(\isotm{Fe}{56})$    & $2.735 \times 10^{8}$   & 2.057  & $6.571 \times 10^{7}$   & 2.474  & $1.183 \times 10^{7}$   \\
\enddata
\end{deluxetable}

\begin{deluxetable}{lllllll}
\tablecaption{\label{table:react_convert_no_T} Convergence ($L_1$ norm) for the reacting convergence with $T$ integration but frozen $c_x$.}
\tablehead{\colhead{field} & \colhead{$\epsilon_{64 \rightarrow 128}$} & 
           \colhead{rate} & \colhead{$\epsilon_{128\rightarrow 256}$} & 
           \colhead{rate} & \colhead{$\epsilon_{256\rightarrow 512}$}}
\startdata
 $\rho$                      & $2.781 \times 10^{18}$  & 2.051  & $6.711 \times 10^{17}$  & 2.580  & $1.122 \times 10^{17}$  \\
 $\rho u$                    & $6.781 \times 10^{26}$  & 2.445  & $1.245 \times 10^{26}$  & 2.907  & $1.659 \times 10^{25}$  \\
 $\rho v$                    & $6.781 \times 10^{26}$  & 2.445  & $1.245 \times 10^{26}$  & 2.907  & $1.659 \times 10^{25}$  \\
 $\rho E$                    & $2.465 \times 10^{35}$  & 2.333  & $4.892 \times 10^{34}$  & 2.650  & $7.794 \times 10^{33}$  \\
 $\rho e$                    & $2.268 \times 10^{35}$  & 2.298  & $4.610 \times 10^{34}$  & 2.722  & $6.988 \times 10^{33}$  \\
 $T$                         & $2.248 \times 10^{21}$  & 1.682  & $7.003 \times 10^{20}$  & 2.439  & $1.291 \times 10^{20}$  \\
 $\rho X(\isotm{He}{4})$     & $2.862 \times 10^{18}$  & 2.027  & $7.023 \times 10^{17}$  & 2.554  & $1.196 \times 10^{17}$  \\
 $\rho X(\isotm{C}{12})$     & $1.717 \times 10^{17}$  & 1.945  & $4.460 \times 10^{16}$  & 2.194  & $9.745 \times 10^{15}$  \\
 $\rho X(\isotm{O}{16})$     & $1.718 \times 10^{14}$  & 1.648  & $5.482 \times 10^{13}$  & 1.898  & $1.471 \times 10^{13}$  \\
 $\rho X(\isotm{Fe}{56})$    & $2.781 \times 10^{8}$   & 2.051  & $6.711 \times 10^{7}$   & 2.580  & $1.122 \times 10^{7}$   \\
\enddata
\end{deluxetable}

\begin{deluxetable}{lllllll}
\tablecaption{\label{table:react_convert_no_T} Convergence ($L_1$ norm) for the reacting convergence with no $T$ integration and calling the EOS.}
\tablehead{\colhead{field} & \colhead{$\epsilon_{64 \rightarrow 128}$} & 
           \colhead{rate} & \colhead{$\epsilon_{128\rightarrow 256}$} & 
           \colhead{rate} & \colhead{$\epsilon_{256\rightarrow 512}$}}
\startdata
 $\rho$                      & $2.781 \times 10^{18}$  & 2.051  & $6.711 \times 10^{17}$  & 2.580  & $1.122 \times 10^{17}$  \\
 $\rho u$                    & $6.781 \times 10^{26}$  & 2.445  & $1.245 \times 10^{26}$  & 2.907  & $1.659 \times 10^{25}$  \\
 $\rho v$                    & $6.781 \times 10^{26}$  & 2.445  & $1.245 \times 10^{26}$  & 2.907  & $1.659 \times 10^{25}$  \\
 $\rho E$                    & $2.465 \times 10^{35}$  & 2.333  & $4.892 \times 10^{34}$  & 2.650  & $7.794 \times 10^{33}$  \\
 $\rho e$                    & $2.268 \times 10^{35}$  & 2.298  & $4.610 \times 10^{34}$  & 2.722  & $6.988 \times 10^{33}$  \\
 $T$                         & $2.248 \times 10^{21}$  & 1.682  & $7.003 \times 10^{20}$  & 2.439  & $1.291 \times 10^{20}$  \\
 $\rho X(\isotm{He}{4})$     & $2.862 \times 10^{18}$  & 2.027  & $7.023 \times 10^{17}$  & 2.554  & $1.196 \times 10^{17}$  \\
 $\rho X(\isotm{C}{12})$     & $1.717 \times 10^{17}$  & 1.945  & $4.460 \times 10^{16}$  & 2.194  & $9.745 \times 10^{15}$  \\
 $\rho X(\isotm{O}{16})$     & $1.718 \times 10^{14}$  & 1.648  & $5.482 \times 10^{13}$  & 1.898  & $1.471 \times 10^{13}$  \\
 $\rho X(\isotm{Fe}{56})$    & $2.781 \times 10^{8}$   & 2.051  & $6.711 \times 10^{7}$   & 2.580  & $1.122 \times 10^{7}$   \\
\enddata
\end{deluxetable}

>>>>

\begin{document}
%======================================================================
% Title
%======================================================================
%\title{A Simplified Spectral Deferred Correction Method for Coupling Hydrodynamics with Reaction Networks and Nuclear Statistical Equilibrium}
\title{Practical Effects of Integrating Temperature with Strang Split Reactions}

@@

%======================================================================
% Abstract and Keywords
%======================================================================
\begin{abstract}
For astrophysical reacting flows, operator splitting is commonly used
to couple hydrodynamics and reactions.  Each process operates
independent of one another, but by staggering the updates in a
symmetric fashion (via Strang splitting) second order accuracy in time
can be achieved.  However, approximations are often made to the
reacting system, including the choice of whether or not to integrate
temperature with the species.  Here we demonstrate through a simple
convergence test that integrating temperature together with reactions
is needed for second-order accuracy.
\end{abstract}

@@

\begin{figure}[t]
\centering
\plotone{test}
\caption{\label{thefigure} our results}
\end{figure}
